Training
========================================================
The time series of the different programmes

```{r, echo = FALSE, message=FALSE, fig.width=10}
library(RCurl)
options(RCurlOptions = list(capath = system.file("CurlSSL",                                              
    "cacert.pem", package = "RCurl"), ssl.verifypeer = FALSE))
myCsv <- getURL("https://docs.google.com/spreadsheet/pub?key=0AjqT5C2L9dEldG0yME8zN0JoNVF2V1d2YnBoTmlVZXc&single=true&gid=1&output=csv")
da <- read.csv(textConnection(myCsv), stringsAsFactors = FALSE)
# Combine the date and time to one column 
da$DT <- as.POSIXct(paste(da[,1], da[,2]), format = "%d/%m/%Y%H:%M:%S")
da[,1] <- as.POSIXct(da[,1], format = "%d/%m/%Y")
da[,1] <- as.POSIXct(da[,2], format = "%H:%M:%S") 
par(mfrow = c(2,3))
for(i in 1:6)
  {da2 <- subset(da, subset = da[,3] == i)
plot(da2$km.min ~ da2$DT, type = 'l', main = paste(c("Times for Level ",
              i)), xlab = "Time", ylab = "KM-Min")
}
```

Now some alternatives that can be changed.  These include km-min with route one and route six without any notes, km-min for all routes with notes as well as the km-min for route one and km-min route six for the last 20 sessions.  The final is 6A.  

```{r, echo=FALSE, message=FALSE, fig.width=10}
par(mfrow = c(2, 3))
da3 <- subset(da, subset = da[, 3] == 1 & da[,13] =="")
# head(da3)
plot(da3$km.min ~ da3$DT, type = 'l', main = "Route 1: no notes", ylab = "km-min",
     xlab = "Date")
da3 <- subset(da, subset = da[, 3] == 6 & da[,13] =="")
# head(da3)
plot(da3$km.min ~ da3$DT, type = 'l', main = "Route 6: no notes", ylab = "km-min", 
     xlab = "Date")
da3 <- subset(da, subset = da[,13] !="")
# head(da3)
plot(da3$km.min ~ da3$DT, type = 'l', main = "All levels with notes", 
     ylab = "km-min", xlab = "Date")
da3 <- subset(da[1:30,], subset = da[,3] == 1)
# head(da3)
plot(da3$km.min ~ da3$DT, type = 'l', main = "Last month: level 1", 
     ylab = "km-min",  xlab = "Date")
da3 <- subset(da[1:30,], subset = da[ ,3] == 6)
# head(da3)
plot(da3$km.min ~ da3$DT, type = 'l', main = "Last month: level 6", 
     ylab = "km-min", xlab = "Date")
da3 <- subset(da, subset = da[,3] == "6A")
#da3
plot(da3$km.min ~ da3$DT, type = 'l', main = "Route 6A", ylab = "kn-min", 
     xlab = "Date")
```
This can also be used to test out the ```dplyr``` package. Also required for this is the manipulation of the ```POSIXct``` and ```POSIXlt``` commands.  Convert to ```POSIXlt``` for full functionality.  Then take the elements such as hours, months etc.

This takes the best km/hour performances for programme one in the afternoon. 
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
da$hour <- as.numeric(as.POSIXlt(da$DT)$hour)
head(filter(da, Prog == "1" & hour >= 12))%>%
  select(km.min, DT)%>%
  arrange(desc(km.min))%>%
head
```